Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-03-14 paper.tex
Description of Pre-sales data
Justification of some decisions in this regard

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}

@@

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Faris$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
           e-mail: {\tt pacv@ugr.es}
}

@@

\begin{minipage}{2.3in} \begin{verbatim}
rest of distributed 1st year
reprints
number of reprints
total returns
returns - dept stores
delegates returns
rest of returns
total returns first year
returns -  dept stores 1st year
delegates returns 1st year
rest of returns 1st year
gifts
units distributed as novelty
total points of sale
points of sale - dept stores
delegates points of sale
rest of points of sale
total points of sale 1st year
dept stores points of sale 1st year
delegates points of sale 1st year
rest of points of sale 1st year
weeks for sale
positive sales environment
medium sales environment
negative sales environment
\end{verbatim} \end{minipage}    \\

@@

%-------------------------------------------------
\subsection{Data collection and analysis}
%FERGU: The first step in our methodology is...

In general, historical data are used to make time series, and from them extracting common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010} (only pre-sales data are available in this problem).
% (Paloma) - Se deberían evitar paréntetis.

In addition, among the variables describing a new book, some may affect 
predictions (those variables provide information), while others may not be 
necessary and even redundant.

>>>>

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}
\usepackage{url}

@@

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Faris$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC, ETSIIT. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
           e-mail: {\tt pacv@ugr.es}
}

@@

\begin{minipage}{2.3in} \begin{verbatim}
rest of distributed 1st year
reprints
number of reprints
total returns
returns - dept stores
delegates returns
rest of returns
total returns 1st year
returns -  dept stores 1st year
delegates returns 1st year
rest of returns 1st year
gifts
units distributed as novelty
total points of sale
points of sale - dept stores
delegates points of sale
rest of points of sale
total points of sale 1st year
dept stores points of sale 1st year
delegates points of sale 1st year
rest of points of sale 1st year
weeks for sale
positive sales environment
medium sales environment
negative sales environment
\end{verbatim} \end{minipage}    \\

@@

%-------------------------------------------------
\subsection{Data collection}

In general, historical data are used to make time series, and from them extracting common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem.

Moreover, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e. those whose value don't depend on the book sales. So, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.

\begin{table}
\caption{Considered pre-sales features and their types. It also shows the names of the variables used in the applied methods.}
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & Input/Output\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  editorial + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods. \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by an editor. In addition, this variable could be interesting to be used to test the prediction model, once it is built. So the editor could try different values for it and see what the predictor yields, in order to take the best decision.

Initially, there were three different features describing the subjects and subsubjects of every book \textit{subject1,2,3} (see Table \ref{tabla:paramsOrig50}), but for most of the patterns (books) there is no value for subjects2 and 3, so we have discarded these features.

Regarding the feature \textit{editorial}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}. In addition, we think it is not really relevant for the accuracy of the models and, moreover, editors will not consider the results in other editorials for predicting its own sales.
% Antonio - Think about this... should we mention this?

Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the editor, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass. So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance. The same reasoning can be applied to subclasses.

%-------------------------------------------------
\subsection{Data preprocessing and initial analysis}

Once a dataset has been composed it must be preprocessed, i.e. it should be revised in order to fix the existing errors (such as wrong or duplicated patterns), or to complete (or address) the absence of information, for instance. The aim is looking for the correctness, homogeneity and completeness of the data.

After this, the features describing every pattern are frequently analysed.
In this case, among the variables describing a new book, some may affect 
predictions (those variables provide information), while others may not be 
necessary and even redundant.
